---
title: "2.POSTER_PRES"
author: "Matthew Bayly"
date: "Sunday, November 06, 2014"
output: html_document
---

## **INDEX**



1. **LM FOR STARTING SIZE & POTENTIAL** & varibale levels
    + 1A: Convert size classes to numerica (increasing)
    +       Work with spring growth only
    +       Work with spring growth only (MID.total.height)
    + 1B: CONVERT D TO ZERO (GROWTH W/SURV)
    + 1C: try with L=3, L=4, M=4, M=3
    + 1D: Predict values to df
    
2. **SPRING GROWTH**
    + 2a MID SUMMER / STARTING POTENTIAL
    + 2b LOOP THROUGH SITES & AVERAGE FOR PLOTS IN SITE
    + 2C REPEAT PROCESS FOR END OF SUMMER GROWTH
    + 2D EXAMIN & CONSIDER?


    
### _Set directories for computer_ ###
```{r}
path.root="C:/Users/DW/Desktop/transplant_analysis/" 
path.dat=paste(path.root, "/Data", sep="") # MAIN DATA FILES
path.dat.raw=paste(path.dat, "/raw_data", sep="") # Don't write here!
path.code=paste(path.root, "/Rcode", sep="") # Source Code
path.obj=paste(path.root, "/Robjects", sep="") # To store temporary objects
path.fig=paste(path.root, "/Figures", sep="") # Polished & exploratory figures

setwd(path.dat); setwd(path.dat.raw); setwd(path.code); setwd(path.fig); setwd(path.obj)
```

Open 2014 plant datafile 
```{r}
setwd(path.dat.raw)
plantdat <- read.csv(file="plantdata.csv")
dim(plantdat); #colnames(plantdat)

# check whole data structure
#str(plantdat)
```


** 1A: Convert size classes to numeric (increasing) **
```{r}
summary(plantdat$MID.total.height) #OK, zero inflated
summary(plantdat$FALL.total.height) #OK, super zero inflated

# remove seeds 
plantdat <- plantdat[ !grepl("SEED", plantdat$pot) , ]
summary(plantdat$pot) 

# replace values
plantdat$pot <- as.character(plantdat$pot)
plantdat$pot[plantdat$pot=="XL"]<-5
plantdat$pot[plantdat$pot=="XS"]<-1
plantdat$pot[plantdat$pot=="S"]<-2

#LARGE & MEDIUM MIGHT HAVE TO SWITCH
plantdat$pot[plantdat$pot=="L"]<-4
plantdat$pot[plantdat$pot=="M"]<-3
plantdat$pot <- as.numeric(plantdat$pot) # BACK TO NUMERIC
summary(plantdat$pot) 

```
** 1B: FIT QUICK LINEAR MODEL spring **
SHOULD HAVE POT(AGE) AND INITIAL START SIZE AS PREDICTOR VARIABLES TO SPRING GROWTH & SURVIVORSHIP. also try with & without zeros

```{r}
# QUICK NORMALITY CHECK 
hist(plantdat$MID.total.height) # nope, definatly not
hist(log(plantdat$MID.total.height + 1)) # hahaha
hist(log(plantdat$start.height + 1)) # hahahah
hist(plantdat$start.height)
# SHOULD TRY WITH & WITHOUT ZEROS 
plantdat$start.height <- log(plantdat$start.height + 1)

# zeros removed & vars log trans
plantdat$FALL.total.height[plantdat$FALL.total.height > 0] <- 1


z1 <- glm(plantdat$FALL.total.height ~ plantdat$start.height + plantdat$pot, family = binomial(link="logit"), data = plantdat)
z2 <- glm(plantdat$FALL.total.height ~ plantdat$start.height + plantdat$pot + plantdat$start.height:plantdat$pot, family = binomial(link="logit"), data = plantdat)  

summary(preddom)
preddom <- plantdat[ ,c('ID', 'FALL.total.height', 'start.height', 'pot')]
preddom <- na.omit(preddom)

mod1.LR=glm(mod.form.quad(preddom,2,3),family=binomial,data=preddom)
mod1.pred=predict(mod1.LR,type="response") # model prediction
mod2.LR=step(mod1.LR,trace=F) # backwards stepwise variable reduction
mod2.pred=predict(mod2.LR,type="response") 
dim(plantdat); dim(preddom); length(mod2.pred)
meggr <- cbind(mod2.pred, preddom)

plot(mod2.pred)


plantdat2 <- merge(plantdat, meggr, by.x = "ID", by.y = "ID", all.x = FALSE, all.y=TRUE)
#tail(plantdat2)
plantdat3 <- plantdat2

plantdat3$fin_sur <- plantdat3$FALL.total.height.y - plantdat3$mod2.pred
hist(plantdat3$fin_sur)

plantdat3$site_fac <- factor(plantdat3$site, levels = c("THOMAS", "MOSBY",  "WILEY", "HUNTER", "CALAPOOIA", "COAST", "LOOK", "ROCK"))
levels(plantdat3$site)
levels(plantdat3$site_fac)
boxplot(plantdat3$fin_sur ~ plantdat3$site_fac, col=c("blue", "green", "blue", "blue", "blue", "yellow", "green", "yellow"))

# average down to plot level for sites

frame <- data.frame(matrix(NA, nrow = 1, ncol = 2))
colnames(frame) <- c("fin_sur", "site")

sites <- c("THOMAS", "MOSBY",  "WILEY", "HUNTER", "CALAPOOIA", "COAST", "LOOK", "ROCK")
for(i in 1:length(sites)){
  current <- plantdat3[which(plantdat3$site==paste(sites[i])), ]
  final <- tapply(current$fin_sur, current$plot, mean)
  final <- data.frame(final)
  final$siteR <- paste(sites[i])
  colnames(final) <- c("fin_sur", "site")
  frame <- rbind(frame, final); rm(final) 
}
str(frame)
head(frame)
tail(frame)
dim(frame)
frame <- frame[2:nrow(frame), ]

frame$site <- factor(frame$site, levels = c("THOMAS", "MOSBY",  "WILEY", "HUNTER", "CALAPOOIA", "COAST", "LOOK", "ROCK"))
boxplot(frame$fin_sur ~ frame$site, col=c("lightblue", "green", "lightblue", "lightblue", "lightblue", "green", "green", "green"), ylab="", xaxt = "n")
axis(1, at=1:8, labels=FALSE)
names <- levels(frame$site)
text(cex=1.1, x=seq(0.6, 7.6, by=1), y=-1, names, xpd=TRUE, srt=45)
frame

###################
#barplots

frame1 <- frame[complete.cases(frame$FALL),] 
frame2 <- tapply(frame1$FALL, frame1$site, mean)
barplot(frame2)



```
